### 2017-12-27 icde/revision/sec-related.tex

%\stitle{Dynamic algorithms}.
Dynamic algorithms have proven useful for various tasks by avoiding computing from scratch~\cite{RamalingamR93}.
To our knowledge, little concern has been paid to dynamic scholarly article ranking except that~\cite{GhoshKHLL11} uses PageRank in dynamic citation networks. However, its solution is based on a strong and impractical assumption that there are no citations between articles in the same years.
Further, although there exist several studies on incremental PageRank computation~\cite{DesikanPSK05,AbiteboulPC03,WuR09} and on incremental PageRank approximation \cite{BahmaniCG10,BahmaniKMU12}, they are not designed for scholarly article ranking.
%
\markedb{In this work, we study dynamic scholarly article ranking in the general case and develop our incremental algorithm in terms of the citation characteristics, which has never been exploited before.}
%Different from previous work, we study scholarly article ranking in a dynamic environment in terms of the citation characteristics of scholarly articles, which has never been exploited before.

>>>>

%\stitle{Dynamic algorithms}.
Dynamic algorithms have proven useful for various tasks by avoiding computing from scratch~\cite{RamalingamR93}.
To our knowledge, little concern has been paid to dynamic scholarly article ranking except that~\cite{GhoshKHLL11} uses PageRank in dynamic citation networks. However, its solution is based on a strong and impractical assumption that there are no citations between articles in the same years.
Further, although there exist several studies on incremental PageRank computation~\cite{DesikanPSK05,AbiteboulPC03,WuR09} and on incremental PageRank approximation \cite{BahmaniCG10,BahmaniKMU12}, they are not designed for scholarly article ranking.
%
\markedb{In this work, we study dynamic scholarly article ranking in the general case and develop our incremental algorithm based on the citation characteristics, which has never been exploited before.}
%Different from previous work, we study scholarly article ranking in a dynamic environment in terms of the citation characteristics of scholarly articles, which has never been exploited before.
